### 2021-04-02 input/experiments.tex
ieee style

This section aims at highlighting the properties of \NAME that enables
adaptive scoped broadcast in dynamic networks. Most importantly, it
aims at answering the following questions: Does \NAME allows the
system to reach consistent partitioning? Does \NAME scales well in
large networks? Does \NAME improves scoped broadcast in
inter-autonomous systems? \TODO{Rework this.} We performed the
experimentation using PeerSim, a simulator written in Java that allows
researchers to evaluate and assess distributed algorithms in large
scale networks~\cite{montresor2009peersim}. The code is available on
the Github platform at
\url{https://github.com/Chat-Wane/peersim-partition}.

\subsection{Convergence and overhead}

\paragraph{Objective:}

To confirm the complexity analysis stating that the overhead in time
and communication depends on current partitioning.

\paragraph{Description:}

We build a network comprising 10k processes. First, we chain processes
together, then we add another communication link per process to
another process. Since links are bidirectional, each process has 4
communication links on average. We set the latency of links between 20
and 40 ms at random following a uniform distribution. We set the
weight of links between 5 and 15 at random following a uniform
distribution. Weights and latency are different, hence the first
$\alpha$ received by a process may not be that of its shortest
path. It implies more concurrent operations, hence more traffic to
reach consistent partitioning.

@@

\paragraph{Results:}

@@

>>>>

This section aims at highlighting the properties of \NAME that enables
adaptive scoped broadcast in dynamic networks. Most importantly, it
aims at answering the following questions: Does \NAME allows the
system to reach consistent partitioning? Does \NAME scales well in
large networks? Does \NAME improves scoped broadcast in
inter-autonomous systems? \TODO{Rework this.} We performed the
experimentation using PeerSim, a simulator written in Java that allows
researchers to evaluate and assess distributed algorithms in large
scale networks~\cite{montresor2009peersim}. The code is available on
the Github platform at
\url{https://github.com/Chat-Wane/peersim-partition}.\TODO{Anonoymous.}

\subsection{Confirm the complexity analysis stating that
  communication and time overheads depend on the current partitioning
  of the system.}

\begin{asparadesc}
\item [Description:] We build a network comprising 10k
  processes. First, we chain processes together, then we add another
  communication link per process to another process. Since links are
  bidirectional, each process has 4 communication links on average. We
  set the latency of links between 20 and 40 ms at random following a
  uniform distribution. We set the weight of links between 5 and 15 at
  random following a uniform distribution. Weights and latency are
  different, hence the first $\alpha$ received by a process may not be
  that of its shortest path. It implies more concurrent operations,
  hence more traffic to reach consistent partitioning.

@@

\item [Results:]

@@

\end{asparadesc}

### 2021-04-02 input/proposal.tex

\begin{definition}[\underline{S}coped broad\underline{cast} (\NAMEB)]
  When Process $x$ scoped \underline{b}roadcasts $b_x(m)$ a
  \underline{m}essage $m$, every correct Process $y$ within a scope
  \underline{r}eceives $r_y(m)$ and \underline{d}elivers it
  $d_y(m)$. The scope depends on \underline{s}tates $\sigma$ of
  processes, \underline{m}etadata $\mu$ within received messages, and
  a \underline{p}redicate $\phi$ verified from process to process:
  $b_x(m) \wedge r_y(m) \implies \exists \pi_{xy} : \forall z \in
  \pi_{xy}, \phi(\mu_z, \sigma_z)$.
\end{definition}

@@

@@

At any time, a process can decide to become a source. \TODO{more.}

\begin{definition}[\underline{C}onsistent \underline{p}artitioning (CP)]
  Let $S \subseteq V$ be the set of \underline{s}ources, $W_{xy} =
  W_{yx}$ be the symmetric \underline{w}eight between $x$ and $y$,
  $\Pi_{xz}$ be the shortest \underline{p}ath from $x$ to $z$ the
  weight of which $|\Pi_{xz}|$ is lower than any other path weight,
  the only consistent partitioning $\mathcal{P}$ is a set of logical
  partitions $P_{s\in S}$ such that each process belongs to a logical
  partition comprising its closest source: $\forall p \in P_{s_1},
  \nexists P_{s_2}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
\end{definition}

%% \begin{theorem}[$SPED \implies CP$]
%%   \underline{S}hortest \underline{p}ath \underline{e}ventual
%%   \underline{d}elivery (SPED) where each process $k_n$ in the shortest
%%   path $\Pi_{ps}: [s, k_1,\ldots,k_n,p]$ eventually deliver the
%%   message forwarded by its predecessor $k_{n-1}$ leads to consistent
%%   partitioning.
%% \end{theorem}

%% \TODO{or:}

\begin{theorem}[\underline{B}est \underline{e}ventual \underline{d}elivery $(BED) \implies CP$]
  Every process eventually delivers, hence forwards, the notification
  message $\alpha_s$ of its best partition $P_s$, eventually leading
  to consistent partitioning.
\end{theorem}

>>>>

\begin{definition}[\label{def:scoped}\underline{S}coped broad\underline{cast} (\NAMEB)]
  When Process $x$ scoped \underline{b}roadcasts $b_x(m)$ a
  \underline{m}essage $m$, every correct Process $y$ within a scope
  \underline{r}eceives $r_y(m)$ and \underline{d}elivers it
  $d_y(m)$. The scope depends on \underline{s}tates $\sigma$ of
  processes, \underline{m}etadata $\mu$ within received messages, and
  a \underline{p}redicate $\phi$ verified from process to process:
  $b_x(m) \wedge r_y(m) \implies \exists \pi_{xy} : \forall z \in
  \pi_{xy}, \phi(\mu_z, \sigma_z)$.
\end{definition}

@@

\input{input/figadd.tex} %% positioning (belong to problem & motivation)

@@

At any time, a process can decide to become a source, hence creating a
new partition in the system by executing an \texttt{Add}
operation. This partition includes at least its source plus
neighboring processes that estimate they are closer to this source
than any other source. Such distance (or \emph{weight}) is
application-dependant. For instance, weights could be latency in live
streaming applications, or differences in profiles for recommendation
systems.

\begin{definition}[\label{def:partitioning}Partitioning]
  Let $S \subseteq V$ be the set of \underline{s}ources, and $P_s$ be
  the \underline{p}artition including at least Process $s$, each
  process belongs to at most one partition $\forall p,q \in V, \forall
  s_1,s_2 \in S: p \in P_{s_1} \wedge q \in P_{s_2} \implies p \neq q
  \vee s_1 = s_2$, and there exists at least one path $\pi_{ps}$ of
  processes that belong to this partition $\forall q \in \pi_{ps}: q
  \in P_s$.
\end{definition}

Definition~\ref{def:scoped} and Definition~\ref{def:partitioning}
share the transitive relevance of process states. However, we further
constrain the partitioning in order to guarantee the existence of
exactly one consistent partitioning that processes eventually converge
to.

\begin{definition}[\underline{C}onsistent \underline{p}artitioning (CP)]
  Let $W_{xy} = W_{yx}$ be the symmetric \underline{w}eight between
  $x$ and $y$, $\Pi_{xz}$ be the shortest \underline{p}ath from $x$ to
  $z$ the weight of which $|\Pi_{xz}|$ is lower than any other path
  weight, the only consistent partitioning $\mathcal{P}$ is a set of
  partitions $P_{s\in S}$ such that each process belongs to a logical
  partition comprising its closest source: $\forall p \in P_{s_1},
  \nexists P_{s_2}$ such that $|\Pi_{s_1p}| > |\Pi_{s_2p}|$.
\end{definition}

Unfortunately, processes do not share a common global knowledge of the
network state. For process to reach consistent partitioning together,
a process becoming a source must notify every process that is closer
to it than any other source. Epidemic
dissemination~\cite{birman1999bimodal} constitutes an efficient
communication pattern to perform such operation.

\begin{theorem}[\underline{B}est \underline{e}ventual \underline{d}elivery $(BED) \implies CP$]
  Assuming reliable communication links, every process eventually
  delivers, hence forwards, the notification message $\alpha_s$ of its
  best partition $P_s$, eventually leading to consistent partitioning.
\end{theorem}
